Analysis of the Anomalous Doppler Effect from Quantum Theory to Classical Dynamics Simulations

### 2025-05-10 paper modification/CPB-tex-template/CPB Template-LaTeX/paper_v2.tex
new updata

\begin{\bm{abstract}}
A quantum model incorporating angular momentum conservation is developed to analyze the Normal and Anomalous Doppler Effects, demonstrating that the resonance condition is strongly influenced by the angular momentum of the wave. The resonance condition involving wave angular momentum is examined numerically, and the energy exchange ratio between the electron’s parallel and gyrokinetic motion during resonance with the electromagnetic wave is simulated, exhibiting strong agreement with quantum theoretical predictions.
\end{abstract}

>>>>

\begin{abstract}
A quantum model incorporating angular momentum conservation is developed to analyze the Normal and Anomalous Doppler Effects, demonstrating that the resonance condition is strongly influenced by the angular momentum of the wave. The resonance condition involving wave angular momentum is examined numerically, and the energy exchange ratio between the electron's parallel and gyrokinetic motion during resonance with the electromagnetic wave is simulated, exhibiting strong agreement with quantum theoretical predictions.
\end{abstract}
